Long name of the paper

### 2018-10-24 anzjs2018/sections/04_implementation.tex
more words

Figure~\ref{fig:timings} shows the timing results for varying number of particles.

@@

To check the model results, 
we need to realise that we are not trying to accurately predict
future locations of the vehicle,
but instead are trying to use a sequence of GPS positions to infer travel
times along intermediate roads.
Therefore, several tools used to assess the validity of a particle filter
are unnecessary.
Instead, we will be comparing the rate of degeneration 
(i.e., the particle sample loses the actual bus and needs to be reinitialized)
and the mean distance between the state estimate and the observation,
[We also explore the uncertainty of travel time estimates,
as well as the variability between consecutive buses]\footnote{assuming we can get the results in time}.

>>>>

Figure~\ref{fig:timings} shows the timing results for varying number of particles.
Nothing too exciting going on here, 
except that writing ETAs takes up the largest chunk of time,
as this involves calculating quantiles which require the estimated ETAs to be sorted,
which is computationally demanding. 
The vehicle update takes the second longest time,
and involves copying particles during the update resampling step.
Finally, predicting the ETAs is pretty quick.
The remaining parts of the application take negligible time,
and all run on a single core to avoid mutex locks.

@@

To check the model results, 
we need to realise that we are not trying to accurately predict
future locations of the vehicle,
but instead are trying to use a sequence of GPS positions to infer travel
times along intermediate roads.
Therefore, several tools used to assess the validity of a particle filter
are unnecessary.
Instead, we will be comparing the rate of degeneration 
(i.e., the particle sample loses the actual bus and needs to be reinitialized)
and the mean distance between the state estimate and the observation; 
we will use the distance between the observation and the route (cross track distance) 
to determine how well the posterior distribution fits the data---%
if the ratio between the CTD and RMSE is large,
then the fit is ``bad''.
[We also explore the uncertainty of travel time estimates,
as well as the variability between consecutive buses]\footnote{assuming we can get the results in time}.

From the Figure~X, 
we see a trade-off between some of the parameters.
Larger values of GPS error decrease the degeneration rate
as well as the rate of resampling (which increases speed);
however, the cost of this is that the mean distance between the posterior distribution
and the observed location increases, giving a less precise estimate of the vehicle's state.
Conversely, the system noise does not have the same effect,
and only slightly effects the values.

So the main way to determine how well everything is working is to look 
at the RMSE of ETAs over time.
